---
title: "The Oscars 2020 - My (Frequentist) Predictions"
author: Alejandro Álvarez 
output: 
   html_document:
      toc: true
      toc_depth: 3
      toc_float:
         collapsed: false
      
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(DT)
library(tm)
library(pdftools)
library(wordcloud2)
library(tidyverse)
library(htmlwidgets)
library(webshot)
library(rmdformats)
library(plotly)

coloresP <- c("#009933","#00e64d","#00cccc","#33ffff",
              "#ace600","#d9ff66","#ffcc00","#e6e600",
              "#ff9900","#ff3300","#ff0066","#990099",
              "#4700b3","#006080","#0099cc","#e600e6",
              "#aa80ff","#333399","#ff80bf","#4dffc3",
              "#00ff00","#80d4ff","#00001a","#004466",
              "#008060","#ff6666")


files <- set_names(list.files("Movies/",
                              pattern = "pdf$",
                              full.names = TRUE),
                   str_replace(list.files("Movies/",
                                          pattern = "pdf$",
                                          full.names = FALSE),".pdf",""))

movies <- Corpus(URISource(files),readerControl = list(reader = readPDF()))

names(movies) <- str_replace(names(movies),".pdf","")

movies <- tm_map(movies,stripWhitespace)
movies <- tm_map(movies,content_transformer(tolower))
movies <- tm_map(movies,content_transformer(removeNumbers))

dtm <- DocumentTermMatrix(movies,
                          control = list(language = "en"))

wft <- as_tibble(as.matrix(dtm)) %>%
   mutate(MOVIE = row.names(as.matrix(dtm))) %>%
   select(ncol(as.matrix(dtm)) + 1,1:(ncol(as.matrix(dtm)))) %>%
   gather(WORD,FREQ,-MOVIE) %>%
   filter(!str_detect(WORD,"https:") & !str_detect(WORD,"leaderboard:")) %>%
   mutate(N_PRIZE = if_else(!is.na(str_extract(WORD,":")),1,0)*FREQ,
          WORD = str_replace(WORD,":",""),
          WORD = str_replace(WORD,"\\(",""),
          WORD = str_replace(WORD,"\\)",""),
          WORD = str_replace(WORD,",","")) %>%
   group_by(MOVIE,WORD) %>%
   summarise_all(sum) %>%
   ungroup()


```

***

**Predictions of the winners of the 92nd Academy Awards, based on the number of awards the nominees have won in each category, in international film festivals during the 2019 - 2020 award season.**

The following categories were not analyzed due to a lack of data: 

* Original Song
* Animated Short Film
* Live Action Short Film
* Documentary Short Subject
* Costume Design

Source: https://editorial.rottentomatoes.com/article/awards-leaderboard-top-movies-of-2019/.

# Total Awards 2019 - 2020


***
<center>
**Total awards by film**

```{r}

n_prizes <- wft %>%
   group_by(MOVIE) %>%
   summarise(N_PRIZE = sum(N_PRIZE)) %>%
   arrange(-N_PRIZE) %>% 
   rename("# awards" = N_PRIZE,"Film" = MOVIE) %>% 
   ggplot(aes(x = reorder(Film,-`# awards`),y = `# awards`)) +
   geom_col(fill = coloresP[14]) +
   theme(axis.text.x = element_text(angle = 90),
         axis.ticks = element_blank()) +
   theme(panel.background = element_blank(),
         panel.grid = element_blank()) +
   xlab("\n\n\n Film") + 
   ylab("\n Total awards won") 

ggplotly(n_prizes,tooltip = c("y"))

```

```{r}

wft %>%
   group_by(MOVIE) %>%
   summarise(N_PRIZE = sum(N_PRIZE)) %>%
   arrange(-N_PRIZE) %>% 
   rename("# awards" = N_PRIZE,"Film" = MOVIE) %>% 
   datatable(rownames = FALSE, 
             filter = "top",
             width = 400,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10,15),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

# Predictions

## Best Picture
***
**Nominees:**

```{r results='asis'}

nominees <- c("Ford v Ferrari","The Irishman","Jojo Rabbit","Joker","Little Women",
              "Marriage Story","1917","Once ... Hollywood","Parasite")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}


f_mov_tag <- unique(wft$WORD[(str_detect(wft$WORD,"internat") | str_detect(wft$WORD,"foreig") | str_detect(wft$WORD,"asia") | str_detect(wft$WORD,"non-engl") | str_detect(wft$WORD,"non-engl"))])

best_pict <- wft %>%
   filter((str_detect(WORD,"pict") | str_detect(WORD,"fil") | str_detect(WORD,"internat") | str_detect(WORD,"foreig") | str_detect(WORD,"asia") | str_detect(WORD,"non-engl")),
          MOVIE %in% nominees) %>%
   mutate(FOREIGN = if_else(WORD %in% f_mov_tag,1,0)*FREQ) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ),
             FR_FREQ = sum(FOREIGN)) %>% ungroup() %>%
   mutate(BM_FREQ = FREQ - 2*FR_FREQ) %>%
   select(MOVIE,BM_FREQ) %>%
   rename("word" = MOVIE, "freq" = BM_FREQ) %>%
   arrange(-freq)

best_pict$freq[best_pict$word == "Parasite"] <- best_pict$freq[best_pict$word == "Parasite"] + 14 - 2 

best_pict$freq[best_pict$word == "1917"] <- best_pict$freq[best_pict$word == "1917"] - 1 

best_pict$freq[best_pict$word %in% c("The Irishman","Little Women",
              "Marriage Story","1917","Once ... Hollywood","Parasite")] <- best_pict$freq[best_pict$word %in% c("The Irishman","Little Women",
              "Marriage Story","1917","Once ... Hollywood","Parasite")] + 2 

best_pict$freq[best_pict$word %in% c("Jojo Rabbit","Joker")] <- best_pict$freq[best_pict$word %in% c("Jojo Rabbit","Joker")] + 1 

best_pict <- best_pict %>% 
   arrange(-freq)

wordcloud2(data = as.data.frame(best_pict),
           size = 0.6,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_pict %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Directing
***
**Nominees:**

```{r results='asis'}

nominees <- c("The Irishman","Joker","1917","Once ... Hollywood","Parasite")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

best_dir <- wft %>%
   filter(str_detect(WORD,"dir"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_dir,
           size = 0.8,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_dir %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## International Feature Film
***
**Nominees:**

```{r results='asis'}

nominees <- c("Corpus Christi","Honeyland","Les Misérables","Pain and Glory","Parasite")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

f_mov_tag <- unique(wft$WORD[(str_detect(wft$WORD,"internat") | str_detect(wft$WORD,"foreig") | str_detect(wft$WORD,"asia") | str_detect(wft$WORD,"non-engl") | str_detect(wft$WORD,"indepe"))])

best_int_pict <- wft %>%
   filter( str_detect(WORD,"foreig") | str_detect(WORD,"asia") | str_detect(WORD,"non-engl"),
          MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   select(MOVIE,FREQ) %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = as.data.frame(best_int_pict),
           size = 0.9,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_int_pict %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Actress in a Leading Role
***
**Nominees:**

```{r results='asis'}

nominees <- c("Harriet","Marriage Story","Judy","Little Women","Bombshell")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

sup_act_tag <- unique(wft$WORD[str_detect(wft$WORD,"support") ])

best_lea_actress <- wft %>%
   filter((str_detect(WORD,"actre") | str_detect(WORD,"support")),
          MOVIE %in% nominees) %>%
   mutate(SUPP = if_else(WORD %in% sup_act_tag,1,0)*FREQ) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ),
             SUPP_FREQ = sum(SUPP)) %>% ungroup() %>%
   mutate(BLFA_FREQ = FREQ - 2*SUPP_FREQ) %>%
   select(MOVIE,BLFA_FREQ) %>%
   rename("word" = MOVIE, "freq" = BLFA_FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_lea_actress,
           size = 0.65,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')
```

```{r echo = FALSE}

best_lea_actress %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Actor in a Leading Role
***
**Nominees:**

```{r results='asis'}

nominees <- c("Pain and Glory","Once ... Hollywood","Marriage Story","Joker","The Two Popes")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

sup_act_tag <- unique(wft$WORD[str_detect(wft$WORD,"support") ])

best_lea_actor <- wft %>%
   filter((str_detect(WORD,"actor") | str_detect(WORD,"support")),
          MOVIE %in% nominees) %>%
   mutate(SUPP = if_else(WORD %in% sup_act_tag,1,0)*FREQ) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ),
             SUPP_FREQ = sum(SUPP)) %>% ungroup() %>%
   mutate(BLFA_FREQ = FREQ - 2*SUPP_FREQ) %>%
   select(MOVIE,BLFA_FREQ) %>%
   rename("word" = MOVIE, "freq" = BLFA_FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_lea_actor,
           size = 0.6,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_lea_actor %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Actress in a Supporting Role
***
**Nominees:**

```{r results='asis'}

nominees <- c("Richard Jewell","Marriage Story","Jojo Rabbit","Little Women","Bombshell")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**


```{r echo = FALSE, warning = FALSE, message = FALSE}

sup_act_tag <- unique(wft$WORD[str_detect(wft$WORD,"support") ])

best_sup_actress <- wft %>%
   filter((str_detect(WORD,"actre") | str_detect(WORD,"support")),
          MOVIE %in% nominees) %>%
   mutate(SUPP = if_else(WORD %in% sup_act_tag,1,0)*FREQ) %>%
   group_by(MOVIE) %>%
   summarise(SUPP_FREQ = sum(SUPP)) %>% ungroup() %>%
   select(MOVIE,SUPP_FREQ) %>%
   rename("word" = MOVIE, "freq" = SUPP_FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_sup_actress,
           size = 0.5,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')
```

```{r echo = FALSE}

best_sup_actress %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Actor in a Supporting Role
***
**Nominees:**

```{r results='asis'}

nominees <- c("A ... Neighborhood","The Two Popes","The Irishman","Once ... Hollywood")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

sup_act_tag <- unique(wft$WORD[str_detect(wft$WORD,"support") ])

best_sup_actor <- wft %>%
   filter((str_detect(WORD,"actor") | str_detect(WORD,"support")),
          MOVIE %in% nominees) %>%
   mutate(SUPP = if_else(WORD %in% sup_act_tag,1,0)*FREQ) %>%
   group_by(MOVIE) %>%
   summarise(SUPP_FREQ = sum(SUPP)) %>% ungroup() %>%
   select(MOVIE,SUPP_FREQ) %>%
   rename("word" = MOVIE, "freq" = SUPP_FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_sup_actor,
           size = 0.3,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')
```

```{r echo = FALSE}

best_sup_actor %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Original Screenplay
***
**Nominees:**

```{r results='asis'}

nominees <- c("Knives Out","Marriage Story","1917","Once ... Hollywood","Parasite")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**


```{r echo = FALSE, warning = FALSE, message = FALSE}


best_or_scrp <- wft %>%
   filter(str_detect(WORD,"scree"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_or_scrp,
           size = 0.55,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_or_scrp %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Adapted Screenplay
***
**Nominees:**

```{r results='asis'}

nominees <- c("The Irishman","Jojo Rabbit","Joker","Little Women","The Two Popes")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

best_ad_scrp <- wft %>%
   filter(str_detect(WORD,"scree"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_ad_scrp,
           size = 0.45,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_ad_scrp %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Cinematography
***
**Nominees:**

```{r results='asis'}

nominees <- c("The Irishman","1917","Joker","The Lighthouse","Once ... Hollywood")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}


best_cinema <- wft %>%
   filter(str_detect(WORD,"cinematogr"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_cinema,
           size = 0.9,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_cinema %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Animated Feature Film
***
**Nominees:**

```{r results='asis'}

nominees <- c("How ... Dragon","I Lost My Body","Klaus","Missing Link","Toy Story 4")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}


best_anim_pict <- wft %>%
   filter(str_detect(WORD,"animated"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(best_anim_pict,
           size = 0.65,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_anim_pict %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Documentary Feature
***
**Nominees:**

```{r results='asis'}

nominees <- c("American Factory","For Sama","Honeyland","The Cave*","The Edge of Democracy*")

cat(paste('-', nominees), sep = '\n')
```

*No data available.
<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}

nominees <- c("American Factory","For Sama","Honeyland")

best_docu <- wft %>%
   filter(str_detect(WORD,"docume"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(best_docu,
           size = 0.5,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_docu %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>


## Original Score
***
**Nominees:**

```{r results='asis'}


nominees <- c("Joker","Little Women","Marriage Story","1917","Star Wars")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}



best_score <- wft %>%
   filter(str_detect(WORD,"soundtra") | str_detect(WORD,"score"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ) - sum(FREQ[WORD == "soundtrack"])) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_score,
           size = 0.65,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_score %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Production Design
***
**Nominees:**

```{r results='asis'}


nominees <- c("The Irishman","Jojo Rabbit","1917","Once ... Hollywood","Parasite")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}




best_production <- wft %>%
   filter(str_detect(WORD,"produc"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_production,
           size = 0.4,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_production %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>


## Film Editing
***
**Nominees:**

```{r results='asis'}


nominees <- c("The Irishman","Jojo Rabbit","Joker","Ford v Ferrari","Parasite")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}




best_film_edit <- wft %>%
   filter(str_detect(WORD,"editi"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_film_edit,
           size = 0.55,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_film_edit %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>


## Sound (Mixing and Editing)*

***

**Nominees:**

```{r results='asis'}


nominees <- c("Ad Astra","Ford v Ferrari","Joker","1917","Once ... Hollywood","Star Wars")

cat(paste('-', nominees), sep = '\n')
```

*The Mixing and Editing are usually a joint award in other competitions.

<center>

**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}




best_sound <- wft %>%
   filter(str_detect(WORD,"sound") | str_detect(WORD,"music"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ) - sum(FREQ[WORD == "soundtrack"])) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_sound,
           size = 0.3,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_sound %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Visual Effects
***
**Nominees:**

```{r results='asis'}


nominees <- c("Avengers","The Irishman","The Lion King","1917","Star Wars")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}



best_visual <- wft %>%
   filter(str_detect(WORD,"virt") | str_detect(WORD,"visual") | str_detect(WORD,"photore"),MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ) - sum(FREQ[WORD == "visually"])) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_visual,
           size = 0.65,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_visual %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>

## Makeup and Hairstyling
***
**Nominees:**

```{r results='asis'}


nominees <- c("Bombshell","Joker","Judy","Maleficent","1917")

cat(paste('-', nominees), sep = '\n')
```

<center>
**And the Oscar goes (probably) to:**

```{r echo = FALSE, warning = FALSE, message = FALSE}



best_hair_make <- wft %>%
   filter(str_detect(WORD,"hair") | str_detect(WORD,"make") ,MOVIE %in% nominees) %>%
   group_by(MOVIE) %>%
   summarise(FREQ = sum(FREQ)) %>% ungroup() %>%
   rename("word" = MOVIE, "freq" = FREQ) %>%
   arrange(-freq)

wordcloud2(data = best_hair_make,
           size = 0.65,
           gridSize = 10,
           color = sample(coloresP,size = length(coloresP),replace = FALSE),
           backgroundColor = "white",
           shape = 'pentagon')

```

```{r echo = FALSE}

best_hair_make %>% 
   rename("Movie" = word, "Number of awards" = freq) %>% 
   datatable(rownames = FALSE, 
             filter = "none",
             width = 500,
             options = list(pageLength = 5, 
                            scrollX = T,
                            lengthMenu = c(5,10),
                            columnDefs = list(list(className = 'dt-center',
                                                   targets = 0:1))) )
```

</center>
